Covariate analysis of UFL-Mayo-ISB RNASeq from cerebellum

### 2016-01-28 code/Rmd/Mayo_Cerebellum_RNASeq.Rmd

### Data preprocessing
```{r preprocess.data, echo=TRUE}
# Fix metadata
METADATA$AgeAtDeath = gsub("_or_above", "", METADATA$AgeAtDeath)
METADATA$Diagnosis = gsub("Pathologic Aging","Pathologic_Aging", METADATA$Diagnosis)
METADATA <- METADATA %>%
  dplyr::filter(!(SampleID %in% c("742_CER", "11386_CER","11311_CER","1923_CER","11477_CER")))
```
Following five samples were considered outliers and removed 742\_CER, 11386\_CER, 11311\_CER, 1923\_CER, 11477\_CER
```{r preprocess.data1}
indToRetain = intersect(METADATA$SampleID, colnames(COUNT))

@@

```{r summary, results='asis', echo=FALSE}
writeLines('Number of samples in each category are')
tmp = data.frame(summary(COVARIATES$Diagnosis))
colnames(tmp) = "No. of samples"
kable(tmp)
```
```{r get.gene.symbols, cache=TRUE}
# Define biomart object
mart <- useMart(biomart = "ensembl", dataset = "hsapiens_gene_ensembl")

>>>>

### Data preprocessing
```{r preprocess.data, echo=TRUE}
# Fix metadata
METADATA$AgeAtDeath = gsub("_or_above", "", METADATA$AgeAtDeath)
METADATA$Diagnosis = gsub("Pathologic Aging","Pathologic_Aging", METADATA$Diagnosis)
METADATA <- METADATA %>%
  dplyr::filter(!(SampleID %in% c("742_CER", "11386_CER","11311_CER","1923_CER","11477_CER")))
```
Following five samples were considered outliers and removed 742\_CER, 11386\_CER, 11311\_CER, 1923\_CER, 11477\_CER, based on the eucledian distance from other samples and/or seperated on the first 2 PC's
```{r preprocess.data1}
indToRetain = intersect(METADATA$SampleID, colnames(COUNT))

@@

```{r summary, results='asis', echo=FALSE}
writeLines('Number of samples in each category are')
tmp = data.frame(summary(COVARIATES$Diagnosis))
colnames(tmp) = "No. of samples"
kable(tmp)
```
```{r get.gene.symbols, cache=TRUE}
# Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", dataset = "hsapiens_gene_ensembl", host = "www.ensembl.org")
